### 2015-12-11 lower-bound.tex
Move and fix lower bound section

Our upper bounds are of the form $O(\sqrt{\sup_{v \in K} f(v) \sum_{t=1}^T
\|\ell_t\|_*^2})$ where $f$ is any $1$-strongly convex function with respect to
$\|\cdot\|$.  The same upper bound is also achieved by \textsc{FTRL} with a
constant learning rate when the number of rounds $T$ and $\sum_{t=1}^T
\|\ell_t\|_*^2$ is known upfront \cite[Chapter 2]{Shalev-Shwartz-2011}.  The
lower bound is $\Omega(D\sqrt{\sum_{t=1}^T \|\ell_t\|_*^2})$.

>>>>

The upper bounds on regret of \textsc{AdaFTRL} and \textsc{SOLO FTRL} are of
the form $O(\sqrt{\sup_{v \in K} f(v) \sum_{t=1}^T \|\ell_t\|_*^2})$ where $f$
is any $1$-strongly convex function with respect to $\|\cdot\|$.  The same
upper bound is also achieved by \textsc{FTRL} with a constant learning rate
when the number of rounds $T$ and $\sum_{t=1}^T \|\ell_t\|_*^2$ is known
upfront \cite[Chapter 2]{Shalev-Shwartz-2011}.  The lower bound is
$\Omega(D\sqrt{\sum_{t=1}^T \|\ell_t\|_*^2})$.
